Differentiable Neural Computers

### 2018-05-04 Presentation/Presentation.tex
sNN, rNN prework

\begin{frame}{Introduction: Motivation}
	Von Neumann architecture
	\begin{figure}
	\begin{tikzpicture}
		[auto,
		block/.style ={rectangle, draw=mDarkBrown, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em},
		block2/.style ={rectangle, draw=mDarkBrown, thick, fill=mDarkTeal, text width=5em, align=center, rounded corners, minimum height=2em},
		block3/.style ={rectangle, draw=black, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em}]
		\draw (-1,0.63) node[block3] (i) {\textcolor{mDarkTeal}{\sc{input}}};
		\draw (6,0.63) node[block3] (o) {\textcolor{mDarkTeal}{\sc{output}}};

@@

>>>>

\begin{frame}{Introduction: Motivation}
	\alert{Von Neumann architecture}
	\begin{figure}
	\begin{tikzpicture}
		[auto,
		block/.style ={rectangle, draw=mDarkBrown, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em},
		block2/.style ={rectangle, draw=mDarkBrown, thick, fill=mDarkTeal, text width=5em, align=center, rounded corners, minimum height=2em},
		block3/.style ={rectangle, draw=black, thick, fill=gray!20, text width=5em, align=center, rounded corners, minimum height=2em}]
		\draw (-1,0.63) node[block3] (i) {\textcolor{mDarkTeal}{\sc{input}}};
		\draw (6,0.63) node[block3] (o) {\textcolor{mDarkTeal}{\sc{output}}};

@@

\begin{frame}{Introduction: Motivation}
	\begin{minipage}{.4\textwidth}	
	\alert{Simple Neural Net}
	\begin{figure}
	\begin{tikzpicture}[scale=.5]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		% 	\node[] (\alph) at (0,\y) {\name};
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90,inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[gray!90] (\y);}}
	\end{tikzpicture}
	\end{figure}
	\end{minipage}
	\pause
	\hspace{1cm}
	\begin{minipage}{.4\textwidth}	
	\alert{Recurrent Neural Net}
	\begin{figure}
	\begin{tikzpicture}[scale=.25]
		\foreach \y /\alph/\name in {
			0/x1/$x_1$,
		  	-1/x2/$x_2$,
		  	-2/x3/$x_3$,
		  	-4/xM/$x_M$
		 }{
		% 	\node[] (\alph) at (0,\y) {\name};
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (0,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (x..) at (0,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			1/h1/$h_1$,
		  	0/h2/$h_2$,
		  	-1/h3/$h_3$,
		  	-5/hN/$h_N$
		 }{
		 	\node[circle, draw=gray!90, thick, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (4,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (h..) at (4,-3) {\tiny {\vdots}};
		 \foreach \y /\alph/\name in {
			0/y1/$y_1$,
		  	-1/y2/$y_2$,
		  	-2/y3/$y_3$,
		  	-4/yP/$y_P$
		 }{
		 	\node[circle, draw=gray!90, inner sep=0pt,minimum size=3mm,fill=white] (\alph) at (8,\y) {\tiny \textcolor{mDarkTeal}{\name}};
		 }
		 \node (y..) at (8,-3) {\tiny {\vdots}};
		 \foreach \x in {x1, x2, x3, xM}
		 {\foreach \h in {h1, h2, h3, hN}
		 {\draw (\x) edge[dotted, gray!90] (\h);}}
		 \foreach \x in {h1, h2, h3, hN}
		 {\foreach \y in {y1, y2, y3, yP}
		 {\draw (\x) edge[dotted, gray!90] (\y);}}
		 \foreach \h in {h1}
		 {\draw (\h.west) [<-, red] .. controls +(-0.8,0.8) and +(0.8,0.8) .. (\h.east);}
		 \foreach \h in {h1}
		 {\foreach \hh in {h2, h3, hN}
		 {\draw (\h.east) edge[->, red] (\hh.west);}}
	\end{tikzpicture}
	\end{figure}
	\end{minipage}
\end{frame}
